A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-15 text/formal-defnition.tex
Revised general description on staged semantics.

The reduction given above is full reduction and any redexes---even
under quotation---can be reduced in an arbitrary order.  Following
previous work~\cite{}, we introduce (small-step, call-by-value) staged
semantics, where only redexes at stage $\varepsilon$\AI{not quite true
	because of unquote--quote reduction} are reduced, modeling an
implementation.

@@

Values at $\varepsilon$ stage are a $\lambda$-abstraction, a quoted code,
or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
be any term but the body of $\Lambda$-abstraction has to a value.  It
means that the body of $\Lambda$-abstraction must be evaluated.  The
side condition for $\TBL_\alpha v^{A'}$ means that escapes in a value
can appear only under nested quotations (because an escape under a
single quotation will splice the code value into the surrounding
code).  See Hanada and Igarashi~\cite{} for details.

>>>>

The reduction given above is full reduction and any redexes---even
under quotation---can be reduced in an arbitrary order.  
Following previous work~\cite{Hanada2014}, 
we introduce (small-step, call-by-value) staged semantics, 
where only $\beta$-reduction or $\Lambda$-reduction at stage or the outer-most $\blacklozenge$-reduction are allowed, 
modeling an implementation.

@@

Values at $\varepsilon$ stage are a $\lambda$-abstraction, a quoted code,
or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
be any term but the body of $\Lambda$-abstraction has to a value.  It
means that the body of $\Lambda$-abstraction must be evaluated.  The
side condition for $\TBL_\alpha v^{A'}$ means that escapes in a value
can appear only under nested quotations (because an escape under a
single quotation will splice the code value into the surrounding
code).  See Hanada and Igarashi~\cite{Hanada2014} for details.
